---
title: "R Notebook"
output: html_notebook
---

```{r}
# running the assay

library(tidyverse)
n_people <- c(2, 5, 8, 10, 15, 20)
coef1 <- 1.6
coef2 <- -0.01
coef3 <- 5
coef4 <- -0.02
distances <- c(60,90,135,202.5,303.75,455.625)
n_trials <- 35
oneto1000 <- 25
e <- 6
groupcategory = c(1,1,1,1,1,1,2,2,2,2,2,2)
x1 <- distances
z <- coef1 + coef2*x1 +
pr = 1/(1+exp(-z))

coef3s <- c(0.4, 0.8, 1.2, 1.6, 2.0, 2.4, 2.8, 3.2, 3.6)
coef4s <- c(-0.018, -0.016, -0.014, -0.012, -0.010, -0.008, -0.006, -0.004, -0.002)
Datarray <- array(dim=c(length(coef3s), length(coef4s),length(n_people)))


coef3_counter =1
for (coef3 in coef3s) {
  coef4_counter =1
  for (coef4 in coef4s) {
    z1 <- coef3 + coef4*x1
    d = NULL
    pr1 = 1/(1+exp(-z1))
    counter=1
    for (i in n_people) {
      for (j in 1:oneto1000){
        df <- c()
        for (k in 1:i){
          df <- rbind(df, data.frame(x1 = c(rep(distances, 2)),
                                     y = c(rbinom(e,n_trials,pr), rbinom(e,n_trials,pr1)),
                                     groupcategory = groupcategory, id = c(rep(k,12))))
        }
        df_aov <- aov(y~x1*groupcategory+Error(id/(x1*groupcategory)),data=df)
        #df_aov <- aov(y~x1*groupcategory+(1|id), data = df)
        
        df_aov_sum <- summary(df_aov)
        pvalue <- df_aov_sum[[5]]
        pvalue <- pvalue[[1]]["groupcategory","Pr(>F)"]
        
        #df_aov_sum <- summary(df_aov)
        #pvalue <- df_aov_sum[[1]]["groupcategory","Pr(>F)"]
        
        d = rbind(d,data.frame(pvalue))
      }
      count <- plyr::ldply(d,function(c) sum(c<=0.05))
      Datarray[coef3_counter,coef4_counter,counter] <- count$V1/oneto1000
      counter = counter +1
      d = NULL
    }
    coef4_counter = coef4_counter + 1
  }
  coef3_counter = coef3_counter + 1
}



```


```{r}

# plotting the results

for (i in 1:length(n_people)){
  a = Datarray[,,i]
  # Justification controls where the cells are anchored
  df <- expand.grid(x = coef3s, y = coef4s)
  df$z <- c(a)
  # default is compatible with geom_tile()
  ggplot(df, aes(x, y, fill = z)) + geom_raster() + ggtitle("N=",n_people[i])
  ggsave(paste("EMRE_coefficient_assay_N", n_people[i] ,".jpg", sep=""))
}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
