---
title: "Simulations for VR distance experiments"
author: "Matt Nolan"
date: "24/01/2020"
output: html_document
---
```{r}
library(tidyverse)
library(broom)
library(lme4)
set.seed(666)
source("sig_power_functions.R")
```



Evaluate sigmoid functions

y = e^(coef1 + coef2*distance)/(e^(coef1 + coef2*distance)+1)
```{r}
distances <- c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625)*100
coef1 <- 1.6
coef2 <- -0.01
y1 <- exp(coef1 + coef2*distances)/(exp(coef1 + coef2*distances)+1)

sim_data_means <- tibble(dist = distances, y = y1)
ggplot(sim_data_means, aes(dist, y)) +
  geom_point()
```

y = e^(coef1 + coef2*distance + coef3*group)/(e^(coef1 + coef2*distance + coef3*group)+1)
```{r}
distances <- rep(c(60,90,135, 202.5, 303.75, 455.625), 2)
groups <- c(rep(0,6), rep(1,6))
coef1 <- 5
coef2 <- -0.03
coef3 <- 1
y2 <- exp(coef1 + coef2*distances + coef3*groups)/(exp(coef1 + coef2*distances + coef3*groups)+1)

sim_data_means <- tibble(dist = distances, group = groups, y = y2)
ggplot(sim_data_means, aes(dist, y, colour = group)) +
  geom_point()
```

y = e^(coef1 + coef2*distance + coef3*group + coef4*group*distance)/(e^(coef1 + coef2*distance + coef3*group + coef4*group*distance)+1)
```{r}
distances <- rep(c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625), 2)
groups <- c(rep(0,6), rep(1,6))
coef1 <-3
coef2 <- -3
coef3 <- 1
coef4 <- -3
y2 <- exp(coef1 + coef2*distances + coef3*groups + coef4*groups*distances)/(exp(coef1 + coef2*distances + coef3*groups + coef4*groups*distances)+1)

sim_data_means <- tibble(dist = distances, group = groups, y = y2)
ggplot(sim_data_means, aes(dist, y, colour = group)) +
  geom_point()
```
```{r}
# Do the same thing using the make_sig function
distances <- rep(c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625), 2)
groups <- c(rep(0,6), rep(1,6))
sig_data_means <- make_sig(distances, groups, 5, -3, 1, 0.01)
ggplot(sig_data_means, aes(dist, y, colour = group)) +
  geom_point()
```


Generate some synthetic data for a single subject taking 20 trials in each condition.
```{r}
trials <- 20
coef1 <- 5
coef2 <- -3
coef3 <- 1
coef4 <- 0.01


distances <- c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625)

x1 <- rep(distances, trials * 2)          # some continuous variables 
x2 <- c(rep(0, trials * length(distances)), rep(1, trials*length(distances)))

z <- coef1 + coef2*x1 + coef3*x2 + coef4*x1*x2       # linear combination with a bias
pr <- 1/(1+exp(-z))         # pass through an inv-logit function
y <- rbinom(length(x1), 1 , pr)      # bernoulli response variable
 
df <- data.frame(y=y,x1=x1, x2=x2)

probs <- df %>% group_by(x1, x2) %>% summarise(m = mean(y), stdev = sd(y))

ggplot(probs, aes(x1, m)) +
  geom_point(aes(colour = x2)) +
  geom_errorbar(aes(ymin = m + stdev, ymax =  m - stdev, colour = x2))


```




Generata and plot data for a single subject taking multiple trials in each condition.
```{r}
# Mkae some example data for two groups and a given set of coefficients
distances <- c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625)
df_2 <- make_groups(distances = distances, trials = 60) %>%
  mutate(y = pmap_dbl(list(x1, x2, c1 = 5, c2 = -3, c3 = 0, c4 = 0.2), make_i_data)) 

probs <- df_2 %>% group_by(x1, x2) %>% summarise(m = mean(y), stdev = sd(y))

ggplot(probs, aes(x1, m)) +
  geom_point(aes(colour = x2)) +
  geom_errorbar(aes(ymin = m + stdev, ymax =  m - stdev, colour = x2))
```




Fit with logistic regression model
```{r}
# For some values of c3 and c4 (e.g. c3 > 1) the fiting can separate.
mod_1 <- glm(y ~ x1 * x2, data = df_2, family = "binomial")

# An alaternative is Bayesian regression provided by the arm package.
mod_1_B <- arm::bayesglm(y ~ x1*x2, data = df_2, family = "binomial")

summary(mod_1)

summary(mod_1_B)
```




Make data for a group of subjects
```{r}
subjects <- 20
distances <- c(0.6,0.9,1.35, 2.025, 3.0375, 4.55625)
trials <- 20

# Use default values for coefficients
df_group <- generate_i_group(subjects = subjects,
                           distances = distances,
                           trials = trials,
                           c1 = 5,
                           c2 = -3,
                           c3 = 5,
                           c4 = 0.04)
```

Fit data for a group of subjects using either GLM or GLMER.
```{r}
#GLM
mod_group <- glm(y ~ x1*x2, data = df_group, family = "binomial")

summary(mod_group)
#GLMER
mod_group_glmer <- glmer(y ~ x1*x2 + (1|subject), data = df_group, family = "binomial")

summary(mod_group_glmer)
```

Now simulate multiple experiments. We will systematically vary the model coefficients. For each set of model coefficients we will carry out repeated simulations.

A first approach is to fit a model with coefficient for the group and group x distance interaction.
```{r, warning=FALSE}
# First generate the coefficients we want to simulate
# This is the number of times we want to repeat each simulation of an experiment with a given set of coefficients
repeats <- 10

# Test matrix generation function with reduced set of values
test_vals <- generate_coefs(vals_1 = seq(-5, 5, 5), 
                            vals_2 = seq(-0.02, 0.02, 0.02),
                            repeats = 3)

# Test helper_i_glm/glmer. These functions simulate full experiments.
test_glm <- helper_i_glm(trials = 10,
                       c3 = -5,
                       c4 = 0)

test_glmer <- helper_i_glmer_wrap(trials = 10,
                       c3 = -5,
                       c4 = 0)

# CAll the function to carry out the simulated experiment
test_models <- sim_full_i_exp(vals_1 = seq(-5, 5, 5),
  vals_2 = seq(-1, 1, 1),
  subjects = 5,
  repeats = 3,
  trials = 20) 
```


Summarise the results
```{r}
models_sum <- full_i_exp_sum(test_models)
```

Take a look
```{r}
ggplot(models_sum, aes(c3, c4)) +
  geom_tile(aes(fill = glm_x2_thresh_prop))

# ggsave("glm_x2_thresh_prop.jpg")

ggplot(models_sum, aes(c3, c4)) +
  geom_tile(aes(fill = glm_x3_thresh_prop))

#ggsave("glm_x3_thresh_prop.jpg")

ggplot(models_sum, aes(c3, c4)) +
  geom_tile(aes(fill = glmer_x2_thresh_prop))

# ggsave("glmer_x2_thresh_prop.jpg")

ggplot(models_sum, aes(c3, c4)) +
  geom_tile(aes(fill = glmer_x3_thresh_prop))

#ggsave("glmer_x3_thresh_prop.jpg")
```


A second approach is to fit a model for each group. Statistical analyses can then compare the intercept and slope coefficients of the two models.
```{r}
# Test matrix generation function with reduced set of values
test_2_vals <- generate_coefs(vals_1 = seq(5, 7, 1),
                            repeats = 3)

# Test helper_glm/glmer. These functions simulate full experiments.
test_glm <- helper_glm(trials = 10,
                       c1 = 5,
                       c2 = -0.03)

test_glmer <- helper_glmer_wrap(trials = 10,
                       c1 = 5,
                       c2 = -0.03)
```

